A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-25 paper.tex
Updates from Overleaf

\begin{abstract}
    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (c.f. http://www.wormbook.org \citet{corsi2015}). We describe a minimal reaction-diffusion model for the \emph{C. elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}. This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}. \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG. In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion.  Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
    % TODO: expand and inflate; fix grammar, cite Olivares2019
\end{abstract}

@@

Xu et al. used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline). The Fitzhugh-Nagumo model has similar activator nullclines.

>>>>

\begin{abstract}
% Note: this is project https://www.overleaf.com/project/5e984f87a777200001dcff7e

    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (c.f. http://www.wormbook.org \citet{corsi2015}) *** also other ref ***. We describe a minimal reaction-diffusion model for the \emph{C. elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}. This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}. \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG. In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion.  Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
    \citet{olivares2018potential}
    \citet{olivares2019}
    % TODO: expand and inflate; fix grammar, cite Olivares2019, \citet @article{olivares2018potential}

\end{abstract}

@@

Xu et al. described a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline). The Fitzhugh-Nagumo model has similar activator nullclines.
